MSB1015_Assignment 2

### 2019-10-13 MSB1015_Assignment2_SuzannetenHage.Rmd
Section 3: error fix + improved documentation
* Section 3, splitting the data in test/training set gave an error, because an old name (data) was used as input for the functions. This has been fixed by updating the name to data_combined. 
* Made some small improvements in the documentation of section 3, to improve readability and clarity.

---
title: "MSB1015_Assignment 2"
author: "Suzanne ten Hage"
date: "12 october 2019"
output: html_notebook
---

@@

**3. Data pre-processing**
3a) Not all boiling points in the database are in kelvin, which is the SI unit for temperature. Before I continue, I make sure all temperatures are in kelvin.

@@

3b) Combine the descriptors and boiling points in one dataset, so we can use this dataset for the PLS. I remove the columns with (almost) all zeros, because 
```{r}

#Fuse the boiling points from data.raw and descriptors into one dataset. 
data_combined <- data.frame(data_descriptors, data_wikidata$bp)

#Define which columns to remove. 
remove_columns <- c("MDEC.13", "MDEC.14", "MDEC.22", "MDEC.23", "MDEC.24", "MDEC.33", "MDEC.34", "MDEC.44", "MDEO.11", "MDEO.12", "MDEO.22", "MDEN.11", "MDEN.12", "MDEN.13", "MDEN.22", "MDEN.23", "MDEN.33")

#Remove all empty columns from the dataset.
data_combined <- data_combined[ , -which(names(data_combined) %in% remove_columns)]

3c) To be able to test how well the model I train performs, it is necessary to keep a part of our data aside as testing data. In the following code you can easily change the size of the test data by adjusting percentage_test.

@@

#Percentage of data to go into the test-set. 
percentage_test <- 0.25

#Splitting data into a training and test set. 
set.seed(101) 
sample = sample.split(data, SplitRatio = percentage_test)
train = subset(data, sample == FALSE)
test  = subset(data, sample == TRUE)

>>>>

---
title: "MSB1015_Assignment 2"
author: "Suzanne ten Hage"
date: "13 october 2019"
output: html_notebook
---

@@

**3. Data pre-processing**
Before we can use the descriptors and boiling points to train a PLS model, some data pre-processing needs to be done.

**3a)** Not all boiling points in the database are in kelvin, which is the SI unit for temperature. Before I continue, I make sure all temperatures are in kelvin.

@@

**3b)** Combine the descriptors and boiling points in one dataset, so we can use this dataset for the PLS. I remove the columns with (almost) all zeros, because these descriptors do not have much predictive value.

@@

#Fuse the boiling points from data_wikidata and data_descriptors into one dataset. 
data_combined <- data.frame(data_descriptors, data_wikidata$bp)

#Define which columns to remove. To include one of these columns as a predictor, remove the column here.  
remove_columns <- c("MDEC.13", "MDEC.14", "MDEC.22", "MDEC.23", "MDEC.24", "MDEC.33", "MDEC.34", "MDEC.44", "MDEO.11", "MDEO.12", "MDEO.22", "MDEN.11", "MDEN.12", "MDEN.13", "MDEN.22", "MDEN.23", "MDEN.33")

#Remove all chosen columns from the dataset.
data_combined <- data_combined[ , -which(names(data_combined) %in% remove_columns)]

#At the time of writing, this returns a dataframe of 7 variables describing 134 alkanes. 
```

**3c)** To be able to test how well the model I train performs, it is necessary to keep a part of my data aside as testing data.

#Percentage of data to go into the test-set. Change this value to change the relative sizes of the training and test sets.
percentage_test <- 0.25

#Split the data into a training and test set. 
set.seed(101) 
sample = sample.split(data_combined, SplitRatio = percentage_test)
train = subset(data_combined, sample == FALSE)
test  = subset(data_combined, sample == TRUE)

#At the time of writing 134 alkanes are split into a training set of 115 alkanes and test set of 19 alkanes. 
```
